A comprehensive analysis of natural sequence variation within the <i>Arabidopsis

### 2018-05-23 manuscript/manuscript.Rmd
need to add IAA_annotations.csv to package

```{r, fig.height=11}
gene_info <- geneInfoFromFile(
  fname = system.file("shiny-app", "gene_family_data",
                      "IAA_gene_ids.csv", package = "r1001genomes"))
annotation <- readAnnotationFile(filename = system.file("shiny-app", "gene_family_data",
                      "IAA_annotations.csv", package = "r1001genomes"), gene_info = gene_info)
alignment <- alignCDS(gene_info$transcript_ID)
# make an alignment data frame
aln_df <- makeAlnDF(alignment[[2]])

@@

In our analysis of the full IAA gene family, one member of most IAA sister pairs had high nonsynonymous diversity while the other sister was more conserved (Figure IAA phylogeny heat map). In an interspecific comparison between *A. thaliana* and *A. lyrata*, IAA19 is more conserved, while IAA6 has regions of increased sequence divergence upstream of the degron and in the N-terminal half of the PB1 domain [@winkler_variation_2017]. Consistent with these results, our analysis of intraspecific natural variation revealed higher conservation for IAA19 (${\pi_N/\pi_S}$ = 0.55) compared to IAA6 (${\pi_N/\pi_S}$ = 2.3) (Figure IAA phylogeny heat map), and also detected high diversity within the same regions of IAA6 as seen in Winkler et al. (Supp Fig IAA6 diversity plot). 
```{r eval=FALSE}
write.nexus.data(as.matrix(alignment[[2]]), file = "IAAs.nex", format = "protein")
aliscore(as.AAbin(alignment[[2]]), path = "/Volumes/SSD/Applications/ALISCORE_v2.0/Aliscore_v.2.0/")
id <- scan(file = "input.fas_List_random.txt", sep = " ", quiet = TRUE)
AAAlign_no_gaps <- as.matrix(alignment[[2]])[, id]
write.nexus.data(AAAlign_no_gaps, file = "~/Desktop/natural-variation-webtool/manuscript/IAAs.nex", format = "protein")
```
```{bash eval=FALSE}
mb

execute /Volumes/SSD/Users/clayw/Desktop/natural-variation-webtool/manuscript/IAAs.nex
# set IAA33 as the outgroup
outgroup AT5G57420.1

@@

```{r}
tree <- treeio::read.beast(file = "~/Desktop/natural-variation-webtool/manuscript/IAAs.nex.con.tre")

IAA_data <- read.csv("~/Dropbox/natural-variation-webtool/manuscript_IAA_A/Alex_Tree_work/IAAs_table.csv")
#tip_labels need to be in the first column
IAA_data %<>% select(name, everything())
IAA_data$name %<>% as.character()
IAA_data$AGI %<>% as.character()

>>>>

```{r, fig.height=11}
gene_info <- geneInfoFromFile(
  fname = system.file("shiny-app", "gene_family_data",
                      "IAA_gene_ids.csv", package = "r1001genomes"))
#annotation <- readAnnotationFile(filename = system.file("shiny-app", "gene_family_data",
#                      "IAA_annotations.csv", package = "r1001genomes"), gene_info = gene_info)
alignment <- alignCDS(gene_info$transcript_ID)
# make an alignment data frame
aln_df <- makeAlnDF(alignment[[2]])

@@

In our analysis of the full IAA gene family, one member of most IAA sister pairs had high nonsynonymous diversity while the other sister was more conserved (Figure IAA phylogeny heat map). In an interspecific comparison between *A. thaliana* and *A. lyrata*, IAA19 is more conserved, while IAA6 has regions of increased sequence divergence upstream of the degron and in the N-terminal half of the PB1 domain [@winkler_variation_2017]. Consistent with these results, our analysis of intraspecific natural variation revealed higher conservation for IAA19 (${\pi_N/\pi_S}$ = 0.55) compared to IAA6 (${\pi_N/\pi_S}$ = 2.3) (Figure IAA phylogeny heat map), and also detected high diversity within the same regions of IAA6 as seen in Winkler et al. (Supp Fig IAA6 diversity plot). 
```{r eval=FALSE}
write.nexus.data(as.matrix(alignment[[2]]), file = "IAAs.nex", format = "protein")
aliscore(as.AAbin(alignment[[2]]), path = "/Volumes/SSD/Applications/ALISCORE_v2.0/Aliscore_v.2.0/")
id <- scan(file = "input.fas_List_random.txt", sep = " ", quiet = TRUE)
AAAlign_no_gaps <- as.matrix(alignment[[2]])[, id]
write.nexus.data(AAAlign_no_gaps, file = "manuscript/IAAs.nex", format = "protein")
```
```{bash eval=FALSE}
mb

execute manuscript/IAAs.nex
# set IAA33 as the outgroup
outgroup AT5G57420.1

@@

```{r}
tree <- treeio::read.beast(file = "IAAs.nex.con.tre")

IAA_data <- read.csv("IAAs_table.csv")
#tip_labels need to be in the first column
IAA_data %<>% select(name, everything())
IAA_data$name %<>% as.character()
IAA_data$AGI %<>% as.character()
